Exploring Alternative Routes Using Multipath TCP

### 2017-06-04 paper/presentation.tex
presentation: revamp evaluation commentary and points

\begin{frame}
  \frametitle{Types of Experiment}

  \begin{itemize}
  \item Previous work has established that there do exist common scenarios where
    detour routing can improve path characteristics
  \item These experiments do not duplicate results
  \item Answer the following:
    \begin{itemize}
    \item Given a network where an alternative route has better properties, can
      this mechanism effectively use it?
    \item Given a network where there is an alternative route and the potential
      for aggregation, can this mechanism aggregate throughput?
    \item Can this mechanism run without modification on the Internet?
    \end{itemize}
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
  \item Two types of network:
    \begin{itemize}
    \item \textbf{Symmetric:} every link has 10Mbps bandwidth
    \item \textbf{Core-limited:} core links have 10Mbps, access links have 20Mbps
    \end{itemize}
  \item Three variations:
    \begin{itemize}
    \item \textbf{Normal:} no loss
    \item \textbf{Lossy:} 1\% packet loss on Link 2
    \item \textbf{Delayed:} 100ms delay on Link 2
    \end{itemize}
  \item Total of 6 scenarios
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
  \item \textbf{1-Subflow:} MPTCP with no available detours
  \item \textbf{NAT:} Using NAT detour
  \item \textbf{VPN:} Using VPN detour
  \item \textbf{TCP:} TCP over default route
  \item \textbf{TCP(NAT):} TCP via the NAT tunnel
  \item \textbf{TCP(VPN):} TCP via the VPN tunnel
  \end{itemize}
  \note[item]{Don't forget to say we use iperf to measure throughput}
\end{frame}

@@

\FigureSlide{figures/sym.pdf}{
  \begin{itemize}
  \item This is a comparison of throughput on Symmetric, Normal. takeaways:
  \item (1) MPTCP is more variable than TCP
  \item (2) The VPN and NAT approaches don't perform as well when there is
    nothing to gain. This seems to be a result of their overhead and maybe
    congestion control.
  \end{itemize}
}

@@

  \begin{itemize}
  \item MPTCP trials are more variable
  \item Mechanism introduces overhead when there is no potential for gain
  \end{itemize}
\end{frame}

\FigureSlide{figures/sym-lossy.pdf}{
  \begin{itemize}
  \item When a small loss rate is added, the story begins to change.
  \item Suddenly, MPTCP NAT and VPN are performing very comparably to vanilla
    TCP over those same paths
  \item MPTCP 1 subflow takes a huge performance hit
  \end{itemize}
}

@@

  \begin{itemize}
  \item MPTCP trials are more variable
  \item Mechanism introduces overhead when there is no potential for gain
  \item Mechanism performs similarly to TCP over best path when the default path
    has loss
  \end{itemize}
\end{frame}

\FigureSlide{figures/easy.pdf}{
  \begin{itemize}
  \item When there is the potential to aggregate throughput, the story changes
    again.
  \item The mechanism is capable of aggregating nearly all bandwidth
  \end{itemize}
}

@@

  \begin{itemize}
  \item MPTCP trials are more variable
  \item Mechanism introduces overhead when there is no potential for gain
  \item Mechanism performs similarly to TCP over best path when the default path
    has loss
  \item Mechanism can effectively aggregate bandwidth when the network has the
    potential
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
  \item MPTCP trials are more variable
  \item Mechanism introduces overhead when there is no potential for gain
  \item Mechanism performs similarly to TCP over best path when the default path
    has loss
  \item Mechanism can effectively aggregate bandwidth when the network has the
    potential, even in the presence of loss
  \end{itemize}
\end{frame}

\FigureSlide{figures/delayed.pdf}{
  \begin{itemize}
  \item With delayed link, there are some funky interactions with slow slow
    start, but MPTCP still outperforms the best paths
  \end{itemize}
}

@@

  \begin{itemize}
  \item MPTCP trials are more variable
  \item Mechanism introduces overhead when there is no potential for gain
  \item Mechanism performs similarly to TCP over best path when the default path
    has loss
  \item Mechanism can effectively aggregate bandwidth when the network has the
    potential, even in the presence of loss or high latency
  \item<2> NAT consistently outperforms VPN both in MPTCP and TCP, but by a small
    amount.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Types of Experiments}

  \begin{itemize}
  \item Previous work has established that there do exist common scenarios where
    detour routing can improve path characteristics
  \item We simply attempt show mechanism works as expected
  \item Answer the following
    \begin{itemize}
    \item Can we achieve throughput of best available path?
    \item When bandwidth aggregation is possible, can we aggregate path
      bandwidth?
    \item What overheads exist in this mechanism?
    \item Can this mechanism be used across the Internet at higher throughput?
    \end{itemize}
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
  \item Two types of network:
    \begin{itemize}
    \item \textbf{Symmetric:} every link has 10Mbps bandwidth
    \item \textbf{Core-limited:} core links have 10Mbps, access links have 20Mbps
    \end{itemize}
  \item Three variations:
    \begin{itemize}
    \item \textbf{Normal:} no loss
    \item \textbf{Lossy:} 1\% packet loss on Link 2 \note[item]{For lossy, we
        tried 0.5\%, 1\%, 2\%, and 5\%. Both 1 and 2 were reasonable - causing
        decreased throughput but not too bad. 0.5 had nearly no effect. 5 had
        too much of an effect. Can show graphs if interested.}
    \item \textbf{Delayed:} 100ms delay on Link 2 \note[item]{For latency, we
        tried 20 and 50 ms. 100 only just started to show throughput drop,
        likely due to slow start.} \note[item]{Large differences in latency
        affect MPTCP more - needs huge buffers to achieve full potential.}
    \end{itemize}
  \item Workload: send as much data as possible from client to server
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
  \item \textbf{1-Subflow:} MPTCP with no available detours
  \item \textbf{NAT:} Using NAT detour
  \item \textbf{VPN:} Using VPN detour
  \item \textbf{TCP:} TCP over default route
  \item \textbf{TCP(NAT):} TCP via the NAT tunnel
  \item \textbf{TCP(VPN):} TCP via the VPN tunnel
  \end{itemize}
  \note[item]{Don't forget to say we use iperf to measure throughput, and try to
  send lots of data.}
\end{frame}

@@

\FigureSlide{figures/sym.pdf}{
  \begin{itemize}
  \item This is a comparison of throughput on Symmetric, Normal. takeaways:
  \item (1) MPTCP has about 140 kbps overhead compared to standard TCP, or about
    1.5\%
  \item Incidentally, segment size 1460, 28 byte overhead of DSS, puts overhead
    at 1.9\%, so not terribly far off.
  \item (2) NAT has no observable overhead in terms of throughput
  \item (3) VPN has observable overhead. 630kbps overhead, or about 6.6\%
  \item Incidintally, segment size 1337 compared to 1432 is about 6.6\%, so spot
    on!
  \item (4) When VPN used with MPTCP, overhead falls to somewhere between the
    1.5\% and 6.6\%, since data is split across a 1.5\% overhead and 6.6\%
    overhead subflow
  \end{itemize}
}

@@

  \begin{itemize}
  \item MPTCP has 140kbps, or about 1.5\% overhead
  \item VPN approach has overhead of about 6.6\%
  \item Mechanism performs well even when no aggregation benefit possible
  \end{itemize}
\end{frame}

\FigureSlide{figures/sym-lossy.pdf}{
  \begin{itemize}
  \item When a small loss rate is added, the story begins to change.
  \item MPTCP NAT and VPN are performing very comparably to vanilla TCP over
    those same paths
  \item MPTCP 1 subflow takes a bigger performance hit than TCP, likely due to
    its more conservative congestion control
  \item MPTCP NAT and VPN have more variance because ACKS are transmitted on
    both paths and get lost
  \end{itemize}
}

@@

  \begin{itemize}
  \item MPTCP has 140kbps, or about 1.5\% overhead
  \item VPN approach has overhead of about 6.6\%
  \item Mechanism performs well even when no aggregation benefit possible
  \item Mechanism performs similarly to TCP over best path when the default path
    has loss
  \end{itemize}
\end{frame}

\FigureSlide{figures/easy.pdf}{
  \begin{itemize}
  \item When there is the potential to aggregate throughput, the story changes
    again.
  \item The mechanism achieves 98.5\% aggregation for NAT and 98.1\% aggregation
    for VPN
  \end{itemize}
}

@@

  \begin{itemize}
  \item MPTCP has 140kbps, or about 1.5\% overhead
  \item VPN approach has overhead of about 6.6\%
  \item Mechanism performs well even when no aggregation benefit possible
  \item Mechanism performs similarly to TCP over best path when the default path
    has loss
  \item Mechanism can effectively aggregate bandwidth when the network has the
    potential
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
  \item MPTCP has 140kbps, or about 1.5\% overhead
  \item VPN approach has overhead of about 6.6\%
  \item Mechanism performs well even when no aggregation benefit possible
  \item Mechanism performs similarly to TCP over best path when the default path
    has loss
  \item Mechanism can effectively aggregate bandwidth when the network has the
    potential, even in the presence of loss
  \end{itemize}
\end{frame}

\FigureSlide{figures/delayed.pdf}{
  \begin{itemize}
  \item With delayed link, MPTCP has more variance.
  \item Similar to lossy link, ACKS can come on high latency link, blocking
    receive window advance
  \end{itemize}
}

@@

  \begin{itemize}
  \item MPTCP has 140kbps, or about 1.5\% overhead
  \item VPN approach has overhead of about 6.6\%
  \item Mechanism performs well even when no aggregation benefit possible
  \item Mechanism performs similarly to TCP over best path when the default path
    has loss
  \item Mechanism can effectively aggregate bandwidth when the network has the
    potential, even in the presence of loss or high latency
  \item<2> NAT consistently outperforms VPN both in MPTCP and TCP, but by a small
    amount.
  \end{itemize}
\end{frame}
